\documentclass{article}
\usepackage{hyperref}
\usepackage{graphicx}
\begin{document}
	\title{CSC 101- Programming Languages}
	\author{Babalola Favour}
	\maketitle
	\tableofcontents
	\section{Java}
	\subsection{Introduction}
	Java programming language was released in the year 1995 and  was created at Sun Microsystem inc, with James Gosling as the lead researcher. 
	\paragraph{}Source: Britannica
	
	\subsection{Applications  that use java includes}
	\begin{enumerate}
		\item Nasa World Wind
		\item Google
		\item Android OS
		\item Netflix
		\item Spotify
		\item Uber
		\item Amazon
		Gotten from: Javavisited
	\end{enumerate}
	\subsection {Java Integrated Development Environments (IDE) Includes:}
	\begin{enumerate}
		\item Xcode
		\item Eclipse
		\item Visual Studio
		\item AWS Cloud9
		\item My Eclipse
	\end{enumerate}
	Source: Best Java Integrated Development Environments (IDE)
	\subsection{Related Programming Languages includes:}
	\begin{enumerate}
		\item C++
		\item C sharp
		\item Lisp
	\end{enumerate}
	Source: Java Compared with Other Languages
	\section{PHP}
	\subsection{Introduction}
	PHP stands for Hypertext Preprocessor it was formally known as personal home page. It was developed by Rasmus Lerdorf in 1994.
	Source: Education Ecosystem. 
	\subsection{Applications  that use PHP includes:}
	\begin{enumerate}
		\item Moodle
		\item Opencart
		\item Ubercart
		\item Mediawiki
	\end{enumerate}
Source: Invensis
\subsection{PHP Integrated Development Environments (IDE) Includes:}
\begin{enumerate}
	\item Netbean
	\item Phpstorm
	\item Eclipse
	\item Zend Studio
	\item CodeLite
\end{enumerate}
Source: Best PHP Integrated Development Environments(IDE).
\subsection{Related Programming Languages includes:}
\begin{enumerate}
	\item Java
	\item Python
	\item Ruby
\end{enumerate}
Source: Hackr.io
\section{Python}
\subsection{Introduction}
Python Programming Language was developed in the late 1980s but implemented in December 1989 by Guido Van Rossum In the Netherlands.
Source: Wikipedia
\subsection{Applications  that use Python includes:}
\begin{enumerate}
	\item Pandas
	\item NumPy
	\item Vega Strike
	\item Disney's Toontown
\end{enumerate}
Source: Edureka
\subsection{Python Integrated Development Environments (IDE) Includes:}
\begin{enumerate}
	\item Pydev
	\item Vim
	\item Pycharm
	\item Visual Studio Code
	\item Atom
\end{enumerate}
Source: 10 Best Python IDE 
\subsection{Related Programming Languages includes:}
\begin{enumerate}
	\item Java
	\item Perl
	\item Tcl
\end{enumerate}
Source: Python
\section{Ruby}
\subsection{Introduction}
Ruby was created by Yukihiro Matsumoto in the year 1995.  Ruby emphasizes on the need for softwares to be first understood by the programmer then the computer.
Source: Launch school.
\subsection{Applications  that use Ruby includes:}
\begin{enumerate}
	\item AirBnB
	\item Basecamp: Project Management System
	\item Soundcloud
	\item Slide share
	\item Hulu
\end{enumerate}
Source: Edureka10 popular web apps that are built using Ruby.
\subsection{Ruby Integrated Development Environments (IDE) Includes:}
\begin{enumerate}
	\item Rubymine
	\item NetBeans
	\item Eclipse
	\item Aptana Studio
	\item Komodo IDE
\end{enumerate}
Source: What’s the Best Ruby IDE for Web Development in 2019
\subsection{Related Programming Languages includes:}
\begin{enumerate}
	\item Java
	\item Python
	\item PHP
\end{enumerate}
Source:  What is Ruby and what are its top alternatives?

\section{C++}
\subsection{Introduction}
C++ programming language was developed in the year 1979 by Bjarne Stroustrup at Bell Laboratories. It was once called “C with Objects" but later named as C++ by Stroustrup in 1983.
Source: Brief history of C++
\subsection{Applications  that use C++ includes:}
\begin{enumerate}
	\item Linux
	\item Microsoft Windows
	\item Mac OSX
	\item Infosys Finacle
	\item MySQL
\end{enumerate}
Source: C++ Language: Features, Uses, Applications and Advantages
\subsection{C++ Integrated Development Environments (IDE) Includes:}
\begin{enumerate}
	\item Arduino IDE
	\item NetBeans
	\item Particle
	\item CLion
	\item C++ Builder
\end{enumerate}
Source: What’s the Best Ruby IDE for Web Development in 2019
\subsection{Related Programming Languages includes:}
\begin{enumerate}
	\item Java
	\item Python
	\item Ruby
\end{enumerate}
Source: Educba
\section{USEFUL TIPS/ links}
\begin{itemize}
	\item \href{https://youtu.be/PzmNb5HXbZ8}{How to cite a website, book, youtube video and picture in powerpoint.}
	\item \href{https://youtu.be/KFIR4nwZqp8}{History of java in animation}
	\item \href{https://youtu.be/Kn3-8Nq2Ddo}{The complete history of python}
\end{itemize}
\newpage
\textbf THANK YOU
\end{document}